

The various operations of the Fibonacci Heaps are as follows:
\begin{itemize}
	\item Inserting a node
	\item Union of Fibonacci Heaps
	\item Extracting the Minimum Node
	\item Decreasing a key
	\item Deleting a node
\end{itemize}

Let us consider $n$ to be the number of nodes in the Fibonacci Heap.

\subsection{Inserting a node}
In Fibonacci Heap, inserting a node is $O(1)$ operation since it is equivalent to adding a node to a circular, doubly linked list called the root list. The added node has no children and is unmarked.

\subsection{Union of Fibonacci Heaps}
In Union operation, the root list of both the Fibonacci Heaps are united  and the new minimum node is determined. The amortized cost of the union operation is $O(1)$ as well.

\subsection{Extracting the Minimum Node}
In the process of extracting the minimum node, the minimum node is extracted from the Fibonacci Heap. The procedure followed is as follows:
\begin{itemize}
	\item The minimum node's children are added to the root list.
	\item Consolidate the root list by linking roots when they are of equal degree.
	\item Repeat the previous step until at most one root remains of each degree.
\end{itemize}
The amortized cost of extracting a minimum node is $O(\lg{n})$

\subsection{Decreasing a key}
In this process, we decrease the value of the key for an existing node. If the min-heap order is not violated, no changes are required. If the min-heap order is violated, many changes can occur. The procedure followed is as follows:
\begin{itemize}
	\item We cut the node from it's parent.
	\item Add the node to the root list.
	\begin{itemize}
	\item If the parent is not marked: No action taken.
	\item If the parent was already marked, it would be added to the root list as well and this step occurs recursively up the tree until either a root or an unmarked node is found.
	\end{itemize}
\end{itemize}
The amortized cost of decreasing a key is $O(1)$

\subsection{Deleting a node}
Deleting a node is equivalent to decreasing a key and then extracting the minimum node for a Fibonacci Heap and hence it has an amortized cost of $O(\lg{n})$